Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
added echo false

```{r}
election_results <- data.frame(
  Metric = c("Chance of Winning", "Average Electoral Votes"),
  Harris = c("68.8%", "279.21"),
  Trump = c("30.1%", "258.79"),
  stringsAsFactors = FALSE
)

@@

```{r}
knitr::include_graphics(plot_path)

@@

```{r plot-probabilities, echo=FALSE, fig.width=8, fig.height=6}
# Reshape the data for plotting
swing_long <- swing_probs %>%
  pivot_longer(cols = c("Trump", "Harris"), names_to = "Candidate", values_to = "Probability")

>>>>

```{r}
#| fig-cap: Election Prediction Results
#| echo: false
#| warning: false
#| message: false

election_results <- data.frame(
  Metric = c("Chance of Winning", "Average Electoral Votes"),
  Harris = c("68.8%", "279.21"),
  Trump = c("30.1%", "258.79"),
  stringsAsFactors = FALSE
)

@@

```{r}
#| fig-cap: Election Map
#| echo: false
#| warning: false
#| message: false
knitr::include_graphics(plot_path)

@@

```{r plot-probabilities, echo=FALSE, fig.width=8, fig.height=6}
#| echo: false
#| warning: false
#| message: false
# Reshape the data for plotting
swing_long <- swing_probs %>%
  pivot_longer(cols = c("Trump", "Harris"), names_to = "Candidate", values_to = "Probability")
